test

### 2023-02-08 test.Rmd
added AIS plot
still needs editing

## Read in AIS Data
```{r}
rawAIS<- read_csv("Data/AIS_072518_072918.csv")
# need to figure out where to store data
```

@@

### New ggplot wtih bplot as basemap 
```{r}
library(mapproj)
# Get bathymetry (code from Ocean Tracking Network https://www.youtube.com/watch?v=xT2F-Y9bKLk)
bgo <- getNOAA.bathy(lon1 = min(df_all$lon-0.7), lon2 = max(df_all$lon + 0.7),
                     lat1 = min(df_all$lat-0.7), lat2=max(df_all$lat + 0.7), resolution = 1)

@@

# Plot
p <- bplot + 
  geom_path(data = track_BB_OL_10, 
            aes(x=long,y=lat,group=spotID), 
            alpha = 0.5,
            linewidth = 3) + # line width parameter is ignored for some reason
  geom_point(data = track_BB_OL_10, 
             aes(x=long,y=lat,group=spotID, size = OL_125, color = OL_125),
             shape=19, stroke = 4) +
  #formatting  
  scale_color_viridis_c(option = "inferno") +
  scale_size_continuous(range = c(0.1,10)) +
  labs(x=NULL, y=NULL, 
       fill = 'Depth',
       color = 'OL 125')+
  theme(panel.grid = element_blank())
```

```{r}
# Animate
anim = p +
  transition_reveal(along = dateTime)+
  ease_aes('linear')+
  shadow_wake(0.1) +
  ggtitle("Date: {frame_along}")

# Animate with control over frames per second and number of frames
animate(anim, nframes = 70, fps = 3)

>>>>

## Read in AIS Data
```{r}
options(readr.show_col_types = FALSE) # quiet the message
rawAIS<- read_csv("Data/AIS_100118_101018.csv") # Vessel data from 10-01-18 to 10-10-18

# Filter by vessels over 100m in length, remove unnecessary columns
AIS <- rawAIS %>%
  filter(Length >= 100) %>%
  dplyr::select(-SOG,-COG, -CallSign, -IMO, -Cargo, -Draft, -Status)

bbox <- st_bbox(c(xmin = min(drift$lat-0.7), 
            xmax = max(drift$lat + 0.7), 
            ymax = max(drift$long + 0.7), 
            ymin = min(drift$long-0.7)), crs = st_crs(4326))

AIS_sf <- AIS %>%
  st_as_sf(coords = c("LON", "LAT"), crs=4326, remove=F) #%>%
  #st_crop(y = bbox)

# Plot + crop to drift area
ggplot() + 
  geom_point(data = AIS_sf, mapping = aes(x=LON,y=LAT)) + 
  scale_x_continuous(limits = c(min(drift$long-0.7), max(drift$long + 0.7))) + 
  scale_y_continuous(limits = c(min(drift$lat-0.7), max(drift$lat + 0.7)))
```

@@

### New ggplot wtih bplot as basemap 
```{r}
library(mapproj)
drift <- track_BB_OL_10

# Get bathymetry (code from Ocean Tracking Network https://www.youtube.com/watch?v=xT2F-Y9bKLk)
bgo <- getNOAA.bathy(lon1 = min(drift$long-0.7), lon2 = max(drift$long + 0.7),
                     lat1 = min(drift$lat-0.7), lat2=max(drift$lat + 0.7), resolution = 1)

@@

# Plot drift
p <- bplot + 
  geom_path(data = drift, 
            aes(x=long,y=lat,group=spotID), 
            alpha = 0.5) +
  geom_point(data = drift, 
             aes(x=long,y=lat,group=spotID, size = OL_125, color = OL_125),
             shape=19, stroke = 1) +

  #formatting  
  scale_color_viridis_c(option = "inferno") +
  scale_size_continuous(range = c(0.1,10)) +
  labs(x=NULL, y=NULL, 
       fill = 'Depth',
       color = 'OL 125')+
  theme(panel.grid = element_blank())

# Plot AIS
q <- bplot +
  #geom_path(data = AIS_sf, aes(x=LON,y=LAT, group = "VesselName")) + 
  geom_sf(data = AIS_sf, aes(x=LON, y=LAT, color = `VesselName`, size = 0.1), show.legend = FALSE) +
  scale_x_continuous(limits = c(min(drift$long-0.7), max(drift$long + 0.7))) + 
  scale_y_continuous(limits = c(min(drift$lat-0.7), max(drift$lat + 0.7))) +
  labs(x=NULL, y=NULL, 
       fill = 'Depth') +
  theme(panel.grid = element_blank())
```

```{r}
# Animate drift
anim = p +
  transition_reveal(along = dateTime)+
  ease_aes('linear')+
  shadow_wake(0.1) +
  ggtitle("Date: {frame_along}")

# Animate with control over frames per second and number of frames
animate(anim, nframes = 70, fps = 3)
anim_save("drift10.gif")

# Animate AIS
anim = q +
  transition_reveal(along = BaseDateTime)+
  ease_aes('linear') +
  ggtitle("Date: {frame_along}")

# Animate with control over frames per second and number of frames
animate(anim, nframes = 400, fps = 3)
